---
title: "R package for actionable feature tweaking"
author: Satoshi Kato (@katokohaku)
output: 
  html_document:
    keep_md: yes
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE
)
library(mvtnorm)
```

## Overview

an implementation to R-package of 
**Gabriele Tolomei, Fabrizio Silvestri, Andrew Haines, Mounia Lalmas "Interpretable Predictions of Tree-based Ensembles via Actionable Feature Tweaking". KDD 2017. [(arXiv)](https://arxiv.org/abs/1706.06691)**

## Installation

You can install the **featureTweakR** package from [GitHub](https://github.com/katokohaku/featureTweakR).

```{r eval=FALSE}
install.packages("devtools") # if you have not installed "devtools" package
devtools::install_github("hoxo-m/pforeach") # if you have not installed "pforeach" package
devtools::install_github("katokohaku/featureTweakR")
```

The source code for **featureTweakR** package is available on GitHub at
- https://github.com/katokohaku/featureTweakR.

## Examples
### Data preparation
```{r dataPrep, cache=TRUE}
set.seed(777)
require(tidyverse)
require(featureTweakR)

data(spam, package = "kernlab")
dataset <- sample_frac(spam) %>% dataSplit(test.ratio = 0.1)

important.var <- c("charExclamation", "charDollar", "remove", "free", "capitalAve", "capitalLong", "your", "hp")
data.train <- dataset$train %>% select(important.var)
true.y     <- dataset$train[ ,ncol(dataset$train)]
data.test  <- dataset$test  %>% select(important.var) %>% head(50)
```
### Build ensemble learner & Extract rules
After data preparation, just call wrapper function to learn ensemble trees + estimate recommendation rules.
```{r learnModel, cache=TRUE}
es <- learnModel(X.train = data.train, true.y = true.y, ntree = 22)
```
### Suggest recommendation
Based on learnt model, new instances that were predicted *label.from* will be suggested how to **tweaked**
```{r predict, cache=TRUE}
ft <- predict(es, newdata = data.test, label.from = "spam", label.to = "nonspam")
```
### Visualize recommendation
provides ***plots()***

#### Plot individual polcy of tweaking for an instance
```{r plotIndividual, cache=TRUE}
plot(ft, k=4)
```

#### Visualize importance
```{r plotPopulation, cache=TRUE}
plot(ft, type = "direction")
```


